Verifying Demonstrations

### 2018-06-01 paper/SystemModel.tex
modifications of section up to the analysis

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.

% cause identifier
\NewVariable{\cid}{cid}

Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

@@

The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
Another example would be to return the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

>>>>

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.
% cause identifier
\NewVariable{\cid}{cid}
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

@@

The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
Another possibility would be to also have a particular type of witnesses, called trusted witnesses, participating to the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

### 2018-06-01 paper/intro.tex
modifications of section up to the analysis

Our second contribution is an adaptation of the Schnorr's protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr's protocol in the 
\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
knowledge, the first to provide \ac{DB} anonymous credentials.

>>>>

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
%Seb: once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
